A Deeper Analysis into the Trends and Factors of the US's Declining Birth Rates

### 2024-02-13 paper/paper.qmd
added data source information to document

>>>>

The datasets for this paper were acquired through the American Economic Association's paper "The Puzzle of Falling US Birth Rates since the Great Recession" [@citeOriginalReplication], with the aid of data available from Centers for Disease Control and Prevention (CDC) Natality data [@citeCDCNCHS] and CDC SEER's U.S. Population Data [@citeCDCSeer].
